---
title: "Network Synthesis Commentary Graphics"
author: "AMP"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(googlesheets4)
library(googledrive)
```

## Load in manual synthesis dataframe


```{r networks}
networks_summary = googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1xjh_PTFbEathR8v5OOU9wY9yBw6C9JI7du6C0L4f_PM/edit?usp=sharing")
```
Tally up the number of networks that have a coastal site: 
```{r tally}
ns_tally <- networks_summary %>%
  group_by(Coastal.Ecosystem)%>%
  count()
```
## Filter to filled out columns 

This was a manual synthesis, and as such has some gaps. In the process of filling these in based on the OG, non R friendly version and also from the network websites, but this is a work in progress. 

```{r full columns, echo=FALSE}
 # networks_summary_clean = networks_summary %>%
 # mutate(Management.Structure = as.factor(Management.Structure), #1= Bottom-Up, #2 = Directed, #3 Hybrid 
 #        across(everything(), ~ ifelse(is.na(.), 0, .))) %>%
 #     filter(Coastal.Ecosystem == 1) %>%
 #   select(EducationMotivation:PredicitingModelingMotivaiton, PlacebasedHypotheses:CrosssiteExperiments, StandardizedMeasurements:QueryDriveResearchQuestions, Physical:Disturbances, Management.Structure) 

#Need to select variables that make the most sense; acutally need to factorize the individual columns for each thing
#1 Motivation
# columns: EducationMotivation, ConservationMotivation, PolicyManagementMotivatiton, MonitoringObservingMotivation, SynthesisCollaborationMotivation, PredicitingModelingMotivaiton
#2 Approach
#columns: PlacebasedHypotheses,ExperimentalManipulations, EnvironmentalMonitoring,ProcessbasedMeasurements,
# CrosssiteDataAssemblage, CrosssiteExperiments, 
#3 Coordination Strategy
#columns: StandardizedMeasurements, DataCollectionPolicies, DatabaseStandards, StrategicSciencePriorities,
# QueryDriveResearchQuestions
#4 Research Type: 
#columns: Physical, Biological, Chemical, Ecological, Disturbances 
#5 Ecosystem Coverage 
# Filtering for coastal yes for now. 
#6 Funding Type
# Management Structure column for now. 

#THERE HAS TO BE A WAY TO ADD FACTORS FOR ALL POSSIBLE COMBOS OF THESE COLUMNS?!!?!?! Need the internet. I dont want to do this manually...
#maybe a case when something is 1, it pulls the column title? 

networks_summary_clean_1 = networks_summary %>%
mutate(across(everything(), ~ ifelse(is.na(.), 0, .)),
       across(everything( as.character())))

networks_summary_clean = networks_summary %>%
mutate(Motivation.text = case_when(EducationMotivation == 1 ~ "Education",
                        ConservationMotivation == 1 ~ "Conservation",
                        PolicyManagementMotivatiton == 1 ~ "Policy",
                        MonitoringObservingMotivation == 1 ~ "Monitoring",
                        SynthesisCollaborationMotivation == 1 ~ "Synthesis",
                        PredicitingModelingMotivaiton == 1 ~ "Modeling"),
        Approach.text = case_when(PlacebasedHypotheses == 1 ~ "Place-based Hypotheses",
                        ExperimentalManipulations == 1 ~ "Experimental Manipulations",
                        EnvironmentalMonitoring == 1 ~ "Environmental Monitoring",
                        ProcessbasedMeasurements== 1 ~ "Process-based Measurements",
                        CrosssiteDataAssemblage == 1 ~ "Cross-site Data Assemblage",
                        CrosssiteExperiments== 1 ~ "Crosssite Experiments"),
        Coordination.Strategy.text = case_when(StandardizedMeasurements == 1 ~ "Standardized Measurements",
                        DataCollectionPolicies == 1 ~ "Data Collection Policies",
                        DatabaseStandards== 1 ~ "Database Standards",
                        StrategicSciencePriorities== 1 ~ "Strategic Science Priorities",
                        QueryDriveResearchQuestions == 1 ~ "Query Driven Research Questions"),
       Research.Type.text = case_when(Physical == 1 ~ "Physical",
                        Biological == 1 ~ "Biological",
                        Chemical == 1 ~ "Chemical",
                        Ecological == 1 ~ "Ecological",
                        Disturbances == 1 ~ "Disturbances"),
       Management.Structure = as.factor(Management.Structure),
       `Management Structure` = as.numeric(Management.Structure),#1= Bottom-Up, #2 = Directed, #3 Hybrid
       # Geographic = as.factor(Geographic),
       # Geographic.Numeric = as.numeric(Geographic)) %>%
       Motivation.text = as.factor(Motivation.text),
       Motivation = as.numeric(Motivation.text),
       Approach.text = as.factor(Approach.text),
       Approach = as.numeric(Approach.text),
       Coordination.Strategy.text = as.factor(Coordination.Strategy.text),
       `Coordination Strategy` = as.numeric(Coordination.Strategy.text),
        Research.Type.text = as.factor(Research.Type.text),
       `Research Type` = as.numeric(Research.Type.text),
       across(everything(), ~ ifelse(is.na(.), 1, .))
       ) %>%
  select(Motivation, Approach, `Coordination Strategy`, `Management Structure`, `Research Type`)


networks_summary_meta = networks_summary %>%
  mutate(across(everything(), ~ ifelse(is.na(.), 0, .)),
    `CDEON Coordinated Distributed Experiments and Observations` = ifelse(is.na(`CDEON Coordinated Distributed Experiments and Observations`),0,`CDEON Coordinated Distributed Experiments and Observations`),
         `EON Ecological Observatory Networks` = ifelse(is.na(`EON Ecological Observatory Networks`),0,`EON Ecological Observatory Networks`),
         `LTMP Long-Term Monitoring Programs` = ifelse(is.na(`LTMP Long-Term Monitoring Programs`),0,`LTMP Long-Term Monitoring Programs`),
         `LTRN Long-Term Research Networks` = ifelse(is.na(`LTRN Long-Term Research Networks`),0,`LTRN Long-Term Research Networks`),
         `ORC Observational Research Consortia` = ifelse(is.na(`ORC Observational Research Consortia`),0,`ORC Observational Research Consortia`),
  Network.Category= case_when(`CDEON Coordinated Distributed Experiments and Observations` == 1 ~ "CDEON",
                        `EON Ecological Observatory Networks` == 1 ~ "EON",
                        `LTMP Long-Term Monitoring Programs`== 1 ~ "LTMP",
                        `LTRN Long-Term Research Networks` == 1 ~ "LTRN",
                        `ORC Observational Research Consortia` == 1 ~ "ORC"),
Motivation.text = case_when(EducationMotivation == 1 ~ "Education",
                        ConservationMotivation == 1 ~ "Conservation",
                        PolicyManagementMotivatiton == 1 ~ "Policy",
                        MonitoringObservingMotivation == 1 ~ "Monitoring",
                        SynthesisCollaborationMotivation == 1 ~ "Synthesis",
                        PredicitingModelingMotivaiton == 1 ~ "Modeling"),
        Approach.text = case_when(PlacebasedHypotheses == 1 ~ "Place-based Hypotheses",
                        ExperimentalManipulations == 1 ~ "Experimental Manipulations",
                        EnvironmentalMonitoring == 1 ~ "Environmental Monitoring",
                        ProcessbasedMeasurements== 1 ~ "Process-based Measurements",
                        CrosssiteDataAssemblage == 1 ~ "Cross-site Data Assemblage",
                        CrosssiteExperiments== 1 ~ "Crosssite Experiments"),
        Coordination.Strategy.text = case_when(StandardizedMeasurements == 1 ~ "Standardized Measurements",
                        DataCollectionPolicies == 1 ~ "Data Collection Policies",
                        DatabaseStandards== 1 ~ "Database Standards",
                        StrategicSciencePriorities== 1 ~ "Strategic Science Priorities",
                        QueryDriveResearchQuestions == 1 ~ "Query Driven Research Questions"),
       Research.Type.text = case_when(Physical == 1 ~ "Physical",
                        Biological == 1 ~ "Biological",
                        Chemical == 1 ~ "Chemical",
                        Ecological == 1 ~ "Ecological",
                        Disturbances == 1 ~ "Disturbances"),
       Management.Structure = as.factor(Management.Structure), 
       Motivation = as.factor(Motivation.text), 
       Approach = as.factor(Approach.text), 
       `Coordination Strategy` = as.factor(Coordination.Strategy.text), 
       `Research Type` = as.factor(Research.Type.text)
)
```

```{r filter to coastal}

networks_summary_clean_coastal = networks_summary_clean %>% 
  filter(Coastal.Ecosystem == 1)

networks_summary_meta_coastal = networks_summary_meta %>%
  filter(Coastal.Ecosystem == 1)
```

## Plotting 

Making some figures for the manuscript draft

```{r pca, echo=FALSE}

network_pca = prcomp(networks_summary_clean, retx = TRUE, center = TRUE, scale. = TRUE)

biplot(network_pca)
summary(network_pca)

library(ggfortify)
network_pca_plot <-autoplot(network_pca, data = networks_summary_meta, colour = "Network.Category", size=2,
                          loadings = TRUE, loadings.colour = 'black',
                          loadings.label = TRUE, loadings.label.size = 3)+
cowplot::theme_cowplot()

print(network_pca_plot)
```
```{r nmds, echo=FALSE}

library(vegan)

network_nmds =
  metaMDS(networks_summary_clean,
          distance = "bray",
          k = 3,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE)
# Run 20 stress 0.0902017 
# ... Procrustes: rmse 0.0005480386  max resid 0.002200324 
goodness(network_nmds)
stressplot(network_nmds)

network_nmds %>% ordiplot(type='none') %>% text("sites") 

```




