---
title: "Figure 2 Network Synthesis"
author: "AMP"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(googlesheets4)
library(googledrive)

getwd()
```

```{r load in data}

#hexs_lc_nw <- readxl::read_excel("./hexagons_State_Land_cover_Hazards.xlsx")

hexs_lc_nw <- readxl::read_excel("./hexagons_Ecoregion_TableToExcel.xlsx")
```

```{r summarize by state & lc}

hazards <- hexs_lc_nw %>%
  select(Hurricane:Total_hazards) %>%
  colnames() 

state_lc_nw <- hexs_lc_nw %>%
  select(WSA9_NAME,area_hexagon_sqkm,dominant_LC,Hurricane:Total_hazards,count_coord_distrib_exp_obs:count_reserves_50km) %>%
  as.data.frame() %>%
  group_by(WSA9_NAME,dominant_LC) %>%
  mutate(number_hex = n()) %>%
  ungroup()%>%
 group_by(WSA9_NAME,dominant_LC,number_hex) %>%
 rename_with(.cols=matches(hazards), ~paste0('haz_', .x)) %>%
  dplyr::summarise(across(everything(), sum)) %>%
  ungroup() %>%
  dplyr::mutate(across(starts_with("haz"), ~.x /number_hex),
                across(starts_with("count"), ~.x /number_hex) ) %>%
    group_by(WSA9_NAME, dominant_LC) %>%
   dplyr::mutate(rel_num_all_haz_per_hex= rowSums(pick(haz_Hurricane:haz_SLR), na.rm = TRUE)) %>% #this is the total relative proportion of all hazards per hexagon. for example, 100% of Alabama Hexs are vulnerable to hurricanes, while only 40% are vulnerable to flooding so the sum of this number is the rel number of hazards each hex in that state would be exposed to...
dplyr::mutate(rel_num_all_networks_per_hex= rowSums(pick(count_coord_distrib_exp_obs:count_ecolo_obs_netw_NERRpoly), na.rm = TRUE))

state_lc_haznw_sum <- state_lc_nw %>%
 group_by(WSA9_NAME) %>%
  select(WSA9_NAME,dominant_LC, rel_num_all_haz_per_hex,rel_num_all_networks_per_hex)%>%
    pivot_wider(names_from = dominant_LC, values_from = c(rel_num_all_haz_per_hex,rel_num_all_networks_per_hex))
```
National Wetland Condition Assessment Grouped Ecoregions

https://www.epa.gov/national-aquatic-resource-surveys/ecoregions-used-national-aquatic-resource-surveys

To allow assessment of condition for distinct wetland types across ecoregions with an acceptable degree of statistical certainty (i.e., a sufficient number of sampled sites by wetland type), NWCA further combined the nine aggregated ecoregions into five NWCA ecoregions:

Coastal Plains = Coastal Plains
Eastern Mountains and Upper Midwest = Northern Appalachians + Southern Appalachians + Upper Midwest
Inland Plains = Southern Plains + Temperate Plains + Northern Plains 
Western Mountains = Western Mountains
Xeric = Xeric

```{r ecoregions}
state_lc_nw_eco <- state_lc_nw %>%
  mutate(ecoregion = case_when(
    str_detect(WSA9_NAME, regex("Northern Appalachians|Southern Appalachians|Upper Midwest", ignore_case=TRUE)) ~ "Eastern Mountains and Upper Midwest",
     str_detect(WSA9_NAME, regex("Southern Plains|Temperate Plains|Northern Plains", ignore_case=TRUE)) ~ "Inland Plains",
                              TRUE ~ WSA9_NAME))
```

```{r try with all data}
hexs_lc_nw_all <- hexs_lc_nw %>%
   mutate(ecoregion = case_when(
    str_detect(WSA9_NAME, regex("Northern Appalachians|Southern Appalachians|Upper Midwest", ignore_case=TRUE)) ~ "Eastern Mountains and Upper Midwest",
     str_detect(WSA9_NAME, regex("Southern Plains|Temperate Plains|Northern Plains", ignore_case=TRUE)) ~ "Inland Plains",
                              TRUE ~ WSA9_NAME)) %>%
  select(ecoregion,dominant_LC ,Total_hazards,count_reserves_50km) %>%
    filter(!dominant_LC %in% "water")
```

```{r figures}

region <- c( "Western Mountains","Xeric", "Inland Plains", "Coastal Plains", "Eastern Mountains and Upper Midwest")
region_colors= c("#A87001","#BFD2F9","#A9A800","#FFAA01", "#6CDFEF")

state_lc_nw_eco %>%
  filter(!dominant_LC %in% "water") %>%
  filter(number_hex > 1) %>%
 ggplot(aes(x=rel_num_all_haz_per_hex,
             y=rel_num_all_networks_per_hex, color=factor(ecoregion, levels = region), size=area_hexagon_sqkm))+
   scale_size(range = c(1, 10), name="Total Area sq km") +
   scale_color_manual(values=region_colors) +
 geom_point()+
  theme_classic() +
  labs(x = "Relative Total Number of Hazards per Ecoregion", y = "Relative Number of Network Sites withink 50km per Ecoregion", color = "Ecoregion")

state_lc_nw_eco %>%
  filter(!dominant_LC %in% "water") %>%
  filter(number_hex > 1) %>%
 ggplot(aes(x=rel_num_all_haz_per_hex,
             y=rel_num_all_networks_per_hex, color=dominant_LC, size=area_hexagon_sqkm))+
   scale_size(range = c(1, 10), name="Total Area sq km") +
 geom_point()+
  theme_classic() +
  labs(x = "Relative Total Number of Hazards per Ecoregion", y = "Relative Number of Network Sites withink 50km per Ecoregion", color = "Dominant Land Cover")

 
hexs_lc_nw_all %>%
  ggplot(aes(x=Total_hazards,
             y=count_reserves_50km))+
  geom_hex()+
    theme_classic() +
  labs(x = "Total Number of Hazards", y = "Network Sites withink 50km")

```
hexs_lc_nw_all %>%
#  filter(!dominant_LC %in% "water") %>%
 ggplot(aes(x=Total_hazards,
             y=count_reserves_50km, color=factor(ecoregion)))+
 geom_point()+
  theme_classic() +
  labs(x = "Relative Total Number of Hazards per Ecoregion", y = "Relative Number of Network Sites withink 50km per Ecoregion", color = "Ecoregion")

hexs_lc_nw_all %>%
 # filter(!dominant_LC %in% "water") %>%
 ggplot(aes(x=count_reserves_50km,
 fill=factor(ecoregion)))+
 geom_density(alpha=0.3)+
  theme_classic() +
  labs(x = "Number of Network Sites withink 50km", y = "Density", fill = "Ecoregion")
  
hexs_lc_nw_all %>%
#  filter(!dominant_LC %in% "water") %>%
  filter(count_reserves_50km == 0) %>%
 ggplot(aes(x=Total_hazards,
 fill=factor(ecoregion)))+
 geom_density(alpha=0.3)+
  theme_classic() +
  labs(x = "Total Number of Hazards", y = "Density", fill = "Ecoregion")

hexs_lc_nw_all %>%
#  filter(!dominant_LC %in% "water") %>%
 ggplot(aes(x=net_haz,
 fill=factor(ecoregion)))+
 geom_density(alpha=0.3)+
  theme_classic() +
  labs(x = "Network Sites within 50km / Total Number of Hazards", y = "Density", fill = "Ecoregion")

+
  labs(x = "Burn Type", y = "Leached Nitrogen \n (mg TDN/ g N)", fill = "Land Coverage")+
   theme(legend.position="none", 
        plot.title =  element_text(size=12), axis.text.y=element_text(size=12,
                                                                     color="black"),
        axis.title.y=element_text(size=12),
        axis.text.x= element_text(size=10, color= "black",angle = 45, hjust = 1),
        axis.title.x=element_text(size=12),
        strip.text = element_blank())+
  facet_wrap(~factor(Land_Coverage_Category,level=veg_order), nrow = 1)+
  theme(strip.background = element_blank())+
  scale_fill_manual(values=color_order2)  + 
  scale_y_continuous(limits=c(0,150),breaks=seq(0,150,50))